This is an example of article title

### 2025-10-30 paper/paper.tex
a few smaller fixes.

The RKMK Heun method is a second order method that can solve ordinary differential equations defined on Lie groups.
A single step of an RKMK-type Heun solver is implemented in Code~\ref{lst:heun}.
The main advantage of using a Lie group solver for this problem is that we do not have to consider parametrization of the Lie group.
The presented approach can be easily generalized to three spatial dimensions, where parametrization of rotations would be even more challenging numerically.

@@

For more advanced methods of solving differential equations on Lie groups in Julia, see
\verb|ManifoldDiffEq.jl|.

>>>>

The RKMK Heun method is a second order method that can solve ordinary differential equations defined on Lie groups.
A single step of an RKMK-type Heun solver is implemented in Code~\ref{lst:heun}.
The main advantage of using a Lie group solver for this problem is that we do not have to consider parametrization of the Lie group.
The presented approach can be easily generalized to three spatial dimensions, where parametrization of rotations on $\mathrm{SO}(3)$ would be even more challenging numerically.

@@

For more advanced methods of solving differential equations on Manifolds and Lie groups in Julia, see
\verb|ManifoldDiffEq.jl|.\footnote{see \href{https://juliamanifolds.github.io/ManifoldDiffEq.jl/stable/}{juliamanifolds.github.io/ManifoldDiffEq.jl/stable/}.}
